\documentclass[a4paper,10pt]{article}

% ---------------------- Packages ----------------------
\usepackage[margin=0.65in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
  pdftitle={Animesh Pandey - Senior Frontend Engineer Resume},
  pdfauthor={Animesh Pandey},
  pdfsubject={Resume},
  pdfkeywords={Senior Frontend Engineer, React, ReactJS, TypeScript, Next.js, JavaScript, Redux, Microfrontends, Design Systems, Accessibility, WCAG, Performance Optimization, SSR, Agentic AI}
}
\usepackage[sfdefault]{roboto}
\renewcommand{\familydefault}{\sfdefault}
\urlstyle{same}
\pagestyle{empty}

% ---------------------- Line spacing & alignment ----------------------
\renewcommand{\baselinestretch}{1.02}
\raggedright

% ---------------------- Section styles -----------------
\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

% ---------------------- List spacing -------------------
\setlist[itemize]{leftmargin=*, label=\textbullet, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt}

% ---------------------- Helper commands ----------------
\newcommand{\companyfirst}[1]{\noindent\textbf{#1}\\[-2pt]}
\newcommand{\company}[1]{\vspace{4pt}\noindent\textbf{#1}\\[-2pt]}
\newcommand{\role}[2]{\textbf{#1}\hfill \textit{#2}\\[-3pt]}
\newcommand{\rolenext}[2]{\vspace{3pt}\textbf{#1}\hfill \textit{#2}\\[-3pt]}

% ---------------------- Document -----------------------
\begin{document}

{\Huge \textbf{Animesh Pandey}}\\[2pt]
{\large Senior Frontend Engineer}\\[4pt]

\sloppy
\href{mailto:animeshpandey1909@gmail.com}{animeshpandey1909@gmail.com} \quad | \quad
+91-8318717926 \quad | \quad
\href{https://linkedin.com/in/pandeyanimesh}{linkedin.com/in/pandeyanimesh} \quad | \quad
Bangalore, India \quad | \quad
\href{https://anmshpndy.com}{anmshpndy.com}

% ===== Summary =====
\section*{Summary}
\textbf{Senior Frontend Engineer} with \textbf{7+ years} of experience building scalable, high-performance SaaS platforms and enterprise applications across analytics, automotive retail, and geospatial domains.
Expert in \textbf{ReactJS}, \textbf{TypeScript}, and modern frontend platform engineering with deep experience in \textbf{design systems}, \textbf{microfrontends}, \textbf{SSR}, \textbf{accessibility}, and \textbf{performance optimization}.
Proven track record of shipping customer-facing platforms serving \textbf{50k+ daily users}, driving engineering efficiency through \textbf{AI-powered automation}, and leading teams on scalable UI infrastructure, testing strategy, and product-thinking-driven development.

% ===== Highlights =====
\section*{Highlights}
\begin{itemize}
  \item Delivered scalable frontend platform systems powering enterprise SaaS products and customer workflows for \textbf{50k+ daily active users}.
  \item Built reusable design systems, \textbf{Storybook}-documented component libraries, and frontend standards — reducing duplicate code by \textbf{25\%} and improving delivery velocity across multiple squads.
  \item Introduced \textbf{AI-driven engineering workflows} (Agentic AI, LLM-assisted tooling) that reduced repetitive developer effort by \textbf{30\%}, freeing engineers for higher-leverage product work.
  \item Led frontend architecture modernization across analytics dashboards, microfrontends, and performance-critical reporting interfaces — improving load times by up to \textbf{30\%}.
\end{itemize}

% ===== Skills =====
\section*{Skills}
\textbf{Frontend:} React / ReactJS, Next.js, TypeScript, JavaScript, HTML5, CSS3, Redux, Angular, React Native, Tailwind CSS \\
\textbf{Architecture \& Platform:} Microfrontends, Design Systems, SSR, Storybook, Module Federation, Performance Budgets, Accessibility (WCAG 2.1 -- Web Content Accessibility Guidelines), Responsive Design \\
\textbf{Testing:} Jest, React Testing Library, Playwright, Cypress, Unit / Integration / E2E Testing \\
\textbf{Build \& Tooling:} Webpack, Vite, GitHub Actions, CI/CD, Git, Docker, Agile, Scrum \\
\textbf{Analytics \& Data Viz:} REST APIs, Highcharts, Leaflet, D3.js, Reporting Platforms, A/B Testing \\
\textbf{Backend \& Cloud:} Node.js, Express, Microservices, AWS, Azure \\
\textbf{AI/Automation:} Agentic AI, OpenAI API, LangChain, GitHub Copilot, LLM-powered Developer Tooling \\
\textbf{Languages:} JavaScript, TypeScript, Python, Java

% ===== Work Experience =====
\section*{Work Experience}

\companyfirst{Lifesight, Bangalore}
\role{Senior Software Engineer}{Dec 2025 -- Present}
\begin{itemize}
  \item Leading frontend platform development for \textbf{Lifesight's Unified Measurement OS} — a marketing intelligence SaaS combining \textbf{MMM (marketing mix modeling)}, incrementality testing, and causal attribution, enabling enterprise brands to optimize campaign ROI and customer journey insights across channels.
  \item Contributing to the frontend of \textbf{Mia}, Lifesight's agentic AI marketing intelligence agent — surfacing AI-driven recommendations from unified measurement data through interactive, data-rich UI experiences.
  \item Architected scalable, \textbf{SSR-capable analytics dashboards} and reporting workflows using \textbf{ReactJS}, \textbf{TypeScript}, and \textbf{Next.js}, optimized for high-volume enterprise datasets and fast time-to-insight.
  \item Established \textbf{performance budgets} and frontend observability practices — including \textbf{Lighthouse} audits, Core Web Vitals monitoring, and bundle optimization — ensuring responsive, reliable interfaces for global enterprise users.
  \item Implemented \textbf{A/B testing} and experimentation infrastructure for growth engineering workflows; drove \textbf{accessibility (WCAG 2.1)} and semantic HTML standards across the platform.
  \item Authored frontend platform standards — reusable UI abstractions, \textbf{Storybook}-driven component libraries, and architecture guidelines — accelerating delivery across analytics and growth engineering squads.
  \item Introduced \textbf{automated testing practices} (unit, integration, E2E) using \textbf{Jest}, \textbf{React Testing Library}, and \textbf{Playwright}, significantly improving release confidence and reducing regression cycles.
  \item Partnered cross-functionally with product, data, and backend teams in an \textbf{Agile/Scrum} environment to translate attribution and analytics requirements into intuitive, high-performance user experiences.
  \item Mentored engineers on frontend architecture, performance optimization, and scalable component-driven development; led architecture reviews and defined team-wide engineering best practices.
\end{itemize}

\company{Tekion, Bangalore}
\role{Software Engineer}{Apr 2022 -- Sep 2025}
\begin{itemize}
  \item Owned and scaled \textbf{10+ mission-critical frontend modules} across enterprise automotive retail products, driving consistency, reusability, and long-term maintainability.
  \item Designed and implemented \textbf{Storybook}-documented \textbf{UI component libraries}, \textbf{microfrontend architectures} using \textbf{Webpack Module Federation}, and company-wide frontend platform standards — reducing duplicate code by \textbf{25\%}.
  \item Built scalable frontend systems using \textbf{ReactJS}, \textbf{TypeScript}, \textbf{Redux}, and \textbf{Next.js}; integrated \textbf{REST APIs} to support complex enterprise data workflows.
  \item Optimized distributed web applications using lazy loading, code splitting, \textbf{Lighthouse} audits, and bundle optimization — reducing load times by up to \textbf{30\%} for \textbf{50k+ daily active users}.
  \item Automated engineering workflows using \textbf{Agentic AI} and LLM-powered developer tooling (GitHub Copilot, internal automation), reducing repetitive engineering effort by \textbf{30\%} and accelerating sprint throughput.
  \item Championed \textbf{accessibility (WCAG 2.1)}, \textbf{responsive design}, and cross-browser compatibility standards; established \textbf{CI/CD} pipelines via \textbf{GitHub Actions} for reliable, automated release workflows.
  \item Mentored \textbf{8+ engineers} through code reviews, Agile/Scrum sprint planning, and architecture workshops; shaped frontend hiring and onboarding processes.
\end{itemize}

\rolenext{Associate Software Engineer}{Jan 2021 -- Apr 2022}
\begin{itemize}
  \item Developed enterprise automotive retail applications using \textbf{ReactJS}, \textbf{Redux}, and \textbf{React Native} for mobile-first customer experiences.
  \item Built \textbf{20+ reusable UI components} and microfrontend modules documented in \textbf{Storybook}, accelerating feature delivery across engineering teams.
  \item Improved application performance and UX consistency, contributing to increased dealership adoption and positive customer satisfaction scores.
\end{itemize}

\company{Vassar Labs, Hyderabad}
\role{Software Development Engineer}{Jun 2019 -- Jan 2021}
\begin{itemize}
  \item Led frontend development of Kerala-WRIS dashboards using \textbf{Angular 8}, \textbf{Highcharts}, and \textbf{Leaflet}, providing real-time water resource visibility to millions of residents and government stakeholders.
  \item Built geospatial visualization systems enabling faster operational and policy decisions for government clients.
  \item Reduced API overhead by \textbf{30\%} through frontend and network optimization of \textbf{AngularJS} dashboards and reporting systems.
\end{itemize}

\rolenext{Software Development Intern}{May 2018 -- Nov 2018}
\begin{itemize}
  \item Developed a \textbf{SCADA monitoring system} for Andhra Pradesh Water Resources using \textbf{AngularJS} and \textbf{D3.js}, enabling real-time operational dashboards for field teams.
\end{itemize}

% ===== Education =====
\section*{Education}
\companyfirst{Indian Institute of Information Technology, Design and Management (IIITDM) Jabalpur}
\role{B.Tech --- Computer Science and Engineering}{2015 -- 2019 \hspace{4pt} | \hspace{4pt} CPI: \textbf{7.9}}

\end{document}
